### 2023-12-05 manuscript.tex
Added IDR review and charge patterning citations

\section{Introduction}
Intrinsically disordered regions (IDRs) are segments of proteins which lack stable three-dimensional structures and instead exist as ensembles of rapidly interconverting conformations. As a result of this structural heterogeneity, IDRs can interact with diverse binding partners. Often these interactions have high specificity but moderate affinity, which permits the efficient propagation of signals by rapid binding and dissociation~\cite{Zhou2012, Wright2014}. Furthermore, as IDRs readily expose their polypeptide chains, they are enriched in recognition motifs for post-translational modifications which allow environmental or physiological conditions to modulate their interactions. Accordingly, IDRs often act as the ``hubs'' of complex signaling networks by integrating signals from diverse pathways and coordinating interactions~\cite{Dunker2005, Buljan2012}. However, as IDRs are ubiquitous in eukaryotic proteomes, with estimates of the fractions of disordered residues in the human, mouse, and fruit fly proteomes ranging between 22 and 24\%~\cite{Piovesan2020, Piovesan2022}, they are involved in diverse processes~\cite{vanderLee2014} including transcriptional regulation~\cite{Liu2006} and the formation of biomolecular condensates~\cite{Banani2017}.

Despite the prevalence and importance of IDRs in eukaryotic proteomes, associating them with specific molecular functions or biological processes remains a significant challenge. The sequences of IDRs are generally poorly conserved, so traditional bioinformatics approaches which rely on the conservation of amino acid sequences to identify homologous proteins and transfer annotations between them are largely unsuccessful when applied to IDRs. However, several recent studies have demonstrated evidence that IDRs are constrained to preserve ``distributed features'' such as flexibility~\cite{Daughdrill2007}, chemical composition~\cite{Moesa2012}, net charge~\cite{Zarin2017}, or charge distribution~\cite{Beh2012}. Because many sequences can yield a region with a specific composition, for example, this mode of constraint uncouples an IDR's fitness from its strict sequence of amino acids. Furthermore, in contrast to folded regions whose precise contacts and packing geometries are easily disrupted by amino acid substitutions, distributed features are robust to such changes, as individual residues only weakly contribute to a region's fitness. For example, a mutation at one site in an IDR that changes its net charge is easily reversed by subsequent compensatory mutations elsewhere in the region. Thus, under this model the sequences of IDRs can rapidly diverge and still preserve their structural or functional properties.

>>>>

\section{Introduction}
Intrinsically disordered regions (IDRs) are segments of proteins which lack stable three-dimensional structures and instead exist as ensembles of rapidly interconverting conformations~\cite{Holehouse2023}. As a result of this structural heterogeneity, IDRs can interact with diverse binding partners. Often these interactions have high specificity but moderate affinity, which permits the efficient propagation of signals by rapid binding and dissociation~\cite{Zhou2012, Wright2014}. Furthermore, as IDRs readily expose their polypeptide chains, they are enriched in recognition motifs for post-translational modifications which allow environmental or physiological conditions to modulate their interactions. Accordingly, IDRs often act as the ``hubs'' of complex signaling networks by integrating signals from diverse pathways and coordinating interactions~\cite{Dunker2005, Buljan2012}. However, as IDRs are ubiquitous in eukaryotic proteomes, with estimates of the fractions of disordered residues in the human, mouse, and fruit fly proteomes ranging between 22 and 24\%~\cite{Piovesan2020, Piovesan2022}, they are involved in diverse processes~\cite{vanderLee2014} including transcriptional regulation~\cite{Liu2006} and the formation of biomolecular condensates~\cite{Banani2017}.

Despite the prevalence and importance of IDRs in eukaryotic proteomes, associating them with specific molecular functions or biological processes remains a significant challenge. The sequences of IDRs are generally poorly conserved, so traditional bioinformatics approaches which rely on the conservation of amino acid sequences to identify homologous proteins and transfer annotations between them are largely unsuccessful when applied to IDRs. However, several recent studies have demonstrated evidence that IDRs are constrained to preserve ``distributed features'' such as flexibility~\cite{Daughdrill2007}, chemical composition~\cite{Moesa2012}, net charge~\cite{Zarin2017}, or charge distribution~\cite{Beh2012, Sherry2017}. Because many sequences can yield a region with a specific composition, for example, this mode of constraint uncouples an IDR's fitness from its strict sequence of amino acids. Furthermore, in contrast to folded regions whose precise contacts and packing geometries are easily disrupted by amino acid substitutions, distributed features are robust to such changes, as individual residues only weakly contribute to a region's fitness. For example, a mutation at one site in an IDR that changes its net charge is easily reversed by subsequent compensatory mutations elsewhere in the region. Thus, under this model the sequences of IDRs can rapidly diverge and still preserve their structural or functional properties.
